Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-08-24 ms_pre_post.Rmd
Add first two sentences of Fertilisation section to the Model

The probability that a focal female $i$ mates with a male $j$ with which she shares some kinship $k_{ij}$ is calculated by first assigning each male a perceived quality $Q_{ij}$. This quality depends upon whether the female has a strategy of avoiding mating with kin ($M_{p}<0$) or preferring mating with kin ($M_{p}>0$; if $M_{p}=0$, all males are assigned a quality of 1, $Q_{ij}=1$). If a focal female avoids mating with kin, then $Q_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that the perceived quality of a male decreases lineary with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$. If a focal female prefers mating with kin, then $Q_{ij} = M_{p} \times k_{ij} + 1$, meaning that the perceived quality of a male increases with increasingly positive values of $k_{ij}$ and $M_{p}$. After a focal female assigns all males a perceived quality, the sum of all male perceived qualities is calculated, then each male quality is divided by this sum. This transformation results in each male having a relative perceived quality $q_{ij}$, which is constrained to values between zero and one. The value of $q_{ij}$ then defines the probability that a female chooses the male as a mate; female choice is therefore stochastic, meaning that females do not always choose the male of the highest $q_{ij}$. For polyandrous females that choose more than one male mate, mates are chosen iteratively such that $Q_{ij}$ and $q_{ij}$ are re-calculated for each additional mate choice, and with $Q_{ij}$ and therefore $q_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.

>>>>

The probability that a focal female $i$ mates with a male $j$ with which she shares some kinship $k_{ij}$ is calculated by first assigning each male a perceived mate quality $Q^{m}_{ij}$. This quality depends upon whether the female has a strategy of avoiding mating with kin ($M_{p}<0$) or preferring mating with kin ($M_{p}>0$; if $M_{p}=0$, all males are assigned a quality of 1, $Q^{m}_{ij}=1$). If a focal female avoids mating with kin, then $Q^{m}_{ij} = (-M_{p} \times k_{ij} + 1)^{-1}$, meaning that the perceived quality of a male decreases lineary with increasingly positive values of $k_{ij}$ and increasingly negative values of $M_{p}$. If a focal female prefers mating with kin, then $Q^{m}_{ij} = M_{p} \times k_{ij} + 1$, meaning that the perceived quality of a male increases with increasingly positive values of $k_{ij}$ and $M_{p}$. After a focal female assigns all males a perceived quality, the sum of all male perceived qualities is calculated, then each male quality is divided by this sum. This transformation results in each male having a relative perceived mate quality $q^{m}_{ij}$, which is constrained to values between zero and one. The value of $q^{m}_{ij}$ then defines the probability that a female chooses the male as a mate; female choice is therefore stochastic, meaning that females do not always choose the male of the highest $q^{m}_{ij}$. For polyandrous females that choose more than one male mate, mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement.

Fertilisation
----------------------------------------------

The fertilisation of a female's $n$ offspring occurs after mating, with each of her $n$ offspring being assigned a sire independently and with replacement from the $N_{males}$ with which the female mated. The probability that a male mate successfully sires an offspring is affected by a female's kinship with the potential sire ($k_{ij}$) and her inbreeding fertilisation strategy ($F_{p}$).
